### 2019-09-23 reports/thesis/chapters/2_dataCollection.tex
Remove Ti

The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test object made of plastic (acrylonitrile butadiene styrene or ABS). The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}. Another test object was manufactured made from titanium (Ti-6Al-4V)

@@

Filters were used, such as a \SI{0.35}{\milli\metre} copper filter and a \SI{2.0}{\milli\metre} tin filter, to tackle beam hardening.

@@

Three datasets were collected and named \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter}. They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections. Projections of the ABS test sample were taken in \texttt{AbsNoFilter} and \texttt{AbsFilter}. The titanium test sample was scanned in \texttt{TiFilter}. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter} and \texttt{TiFilter}.

The properties of each dataset are shown in Table \ref{table:data_dataset}. These include the properties of the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections. A sample of the obtained, simulated and greyscale projections for the datasets \texttt{AbsNoFilter}, \texttt{AbsFilter} and \texttt{TiFilter} are shown in Figures \ref{fig:data_AbsNoFilter}, \ref{fig:data_AbsFilter} and \ref{fig:data_TiFilter} respectively.

\begin{sidewaystable}
\centering
\begin{tabular}{l|lll}
                                                       & \multicolumn{3}{c}{Dataset name}                                                \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             & \texttt{TiFilter}        \\ \hline
potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             & 190                      \\
power (\SI{}{\watt})                                   & 36                   & 20                             & 20                       \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper & \SI{2.0}{\milli\metre} tin \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            & 1415                     \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            & 86                       \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            & 875                      \\
number of replications for each angle                  & 100                  & 20                             & 20                       \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            & 0.0                      \\
\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            & 10                       \\
\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             & 20                       \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             &                          \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             &                          \\
number of replications for each power                  & 20                   & 20                             & 20                    
\end{tabular}
\caption{Properties of the three datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

@@

\begin{figure}[p]
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30.eps}
      \caption{Obtained projection at \SI{20}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilterDeg30_sim.eps}
      \caption{Simulated projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration1.eps}
      \caption{Greyscale projection at \SI{0}{\watt}}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/data/TiFilter_calibration3.eps}
      \caption{Greyscale projection at \SI{20}{\watt}}
    \end{subfigure}
  }
  \caption{\texttt{TiFilter} projections at \ang{30}. The colour scales are in units of \SI{}{\adu}.}
  \label{fig:data_TiFilter}
\end{figure}

>>>>

The \emph{Fortus 400mc (Stratasys, US)} was used to manufacture the test object made of plastic (acrylonitrile butadiene styrene or ABS). The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.

@@

A \SI{0.35}{\milli\metre} copper filter was used to tackle beam hardening.

@@

Two datasets were collected and named \texttt{AbsNoFilter} and \texttt{AbsFilter}. They contain replicate projections of the test sample at two different angles, named $\ang{30}$ and $\ang{120}$, as well as replicate greyscale projections. To investigate the effects of beam hardening, no x-ray filter was used in \texttt{AbsNoFilter}, a filter was used in \texttt{AbsFilter}.

The properties of each dataset are shown in Table \ref{table:data_dataset}. These include the properties of the x-ray tube, the XCT apparatus and what powers were used in the greyscale projections. A sample of the obtained, simulated and greyscale projections from the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} are shown in Figures \ref{fig:data_AbsNoFilter} and \ref{fig:data_AbsFilter} respectively.

\begin{sidewaystable}
\centering
\begin{tabular}{l|ll}
                                                       & \multicolumn{2}{c}{Dataset name}                      \\
                                                       & \texttt{AbsNoFilter} & \texttt{AbsFilter}             \\ \hline
potential difference (\SI{}{\kilo\volt})               & 80                   & 80                             \\
power (\SI{}{\watt})                                   & 36                   & 20                             \\
filter                                                 & no filter            & \SI{0.35}{\milli\metre} copper \\
time exposure (\SI{}{\milli\second})                   & 708                  & 500                            \\
distance from source to object (\SI{}{\milli\metre})   & 217                  & 168                            \\
distance from source to detector (\SI{}{\milli\metre}) & 1178                 & 876                            \\
number of replications for each angle                  & 100                  & 20                             \\ \hline
powers used for greyscale projections (\SI{}{\watt})   & 0.0                  & 0.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 10                   & 5.0                            \\
\multicolumn{1}{c|}{\vdots}                            & 18                   & 10                             \\
\multicolumn{1}{c|}{\vdots}                            & 28                   & 15                             \\
\multicolumn{1}{c|}{\vdots}                            & 36                   & 20                             \\
number of replications for each power                  & 20                   & 20                             
\end{tabular}
\caption{Properties of the three datasets obtained for the experiment.}
\label{table:data_dataset}
\end{sidewaystable}

@@

### 2019-09-23 reports/thesis/chapters/5_inference.tex
Remove Ti

\afterpage{\clearpage}
\section{Results}
The empirical null filter was developed and tested thoroughly on simulated images. In this section, the filter was applied to the projections in the \texttt{AbsFilter} and \texttt{TiFilter} datasets.

\subsection{ABS Test Sample}

@@

\subsection{Titanium Test Sample}

The whole procedure was repeated on the titanium test sample in the dataset \texttt{TiFilter}. The resulting $z$ statistics are shown in Figure \ref{fig:inference_subroiTiFilter_unfiteredZ} and shows, as in the \texttt{AbsFilter} case, a boundary on the edges of the test sample. The faces of the test sample were manually segmented and the empirical null filter was used on each segment separately and stitched together to form the final stages of the analysis.

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_unfilteredZ.eps}
        \caption{\ang{30}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_unfilteredZ.eps}
        \caption{\ang{120}}
      \end{subfigure}
    }
  \caption{Unfiltered $z$ images from the dataset \texttt{TiFilter}}
  \label{fig:inference_subroiTiFilter_unfiteredZ}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}

The resulting inference are shown in Figures \ref{fig:inference_subroiTiFilterDeg30_inference} and \ref{fig:inference_subroiTiFilterDeg120_inference}. Unfortunately the edges of the test sample were falsely tested as positive and none of the voids were detected. The discrepancies are at the edges and can be due to inaccurate face segmentation or poor alignment of the \emph{aRTist} projection to the obtained projection.

@@

The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering. Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}.

Larger voids of diameter \SI{2.4}{\milli\metre} were detected in the ABS test sample. False positives do occur but this is unavoidable because tests were done at the 5\% FDR level. Typically in the experiments, false positives were isolated single pixels and probably occurred due to random chance. Clusters of positive pixels should raise suspicion. One could create a binary image, assigning a Boolean value whether that pixel was tested positive or not. A binary image filter, such as erode followed by a dilate, can be used to remove isolated positive pixels to emphasise the cluster of positive pixels.

@@

While the empirical null filter performed well for the ABS test sample, it failed in the titanium test sample due to dominating effects on the edges. This could be due to poor face segmentation or poor alignment of the \emph{aRTist} projection with the obtained projection. This demonstrates that the empirical null filter can cater for model misspecification but there becomes a point where model misspecified null statistics cannot be distinguished from non-null statistics. Another possible cause for dominating edge effects are metal artifacts such as streaks which are problems observed in XCT of metal parts \citep{deman1998metal, nawaz2014metal}. Lastly, because the titanium test sample was created using a power-based method, powder may become trapped \citep{brierley2018optimized} in the void. This results in the voids appearing with less contrast in the projections, making it harder to detect.

>>>>

\afterpage{\clearpage}
\section{Results}

@@

@@

The empirical null filter demonstrated that it can adjust the null hypotheses according to the data to make sensible inference. In the simulations, it was found that the FDR level is preserved after filtering. Also, the empirical null filter outperformed other methods based on quantiles, as suggested by \cite{efron2004large}. A sensible kernel radius is required to aid distinguishing misspecified null statistics from non-null statistics, for example, a kernel too small would treat defects as the null.

In the experiment, the larger voids of diameter \SI{2.4}{\milli\metre} were detected in the test sample. False positives do occur but this is unavoidable because tests were done at the 5\% FDR level. Typically in the experiments, false positives were isolated single pixels and probably occurred due to random chance. Clusters of positive pixels should raise suspicion. One could create a binary image, assigning a Boolean value whether that pixel was tested positive or not. A binary image filter, such as erode followed by a dilate, can be used to remove isolated positive pixels to emphasise the cluster of positive pixels.

The assessment of the inference could be improved if the location of the defects were known in the projection. This would allow identifying which positives are true and false positives so that the analysis can be quantified using a ROC curve.

@@
